\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png} \\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-5mm}

### 2024-01-20 text/paper/paper.tex
paper.tex

\subsection{Procedure}
    \label{sec:procedure}

We started by displaying the samples in a vertical sample holder with the given order: in the lowest position the implanted sample, followed by lithium aluminate ($\ce{LiAlO2}$) and finally lithium fluoride ($\ce{LiF}$). 
In order to do a calibration we added a triple $\alpha$ source on the holder above the lithium fluoride. 
Using a pachymeter, we measured the distance between the samples so that afterwards we could control the height of the holder in the chamber and change the beam's target.
We placed the sample holder on a support and inserted both of them inside the chamber. 
A vacuum machine was connected to the accelerator to reduce the pressure inside both the chamber and the beam.
Afterwards, we started the procedure to turn on the TANDEM accelerator, according to the provided instruction manual. 
Firstly, we turned on the $\ce{H^+}$ duoplasmatron source of the accelerator as well as the magnets and lenses. 
Then, we opened the valves to propagate the vacuum throughout the entirety of the tubes.
In the control panel, we adjusted the angles of the lenses and the magnets current according to the manual, so that the beam would reach the samples. 
Finally, we used a collimator with a 2mm radius to collimate the beam.
In order to collect the data, we used a computer program to obtain the spectra of the different sources. 
The multichannel analyzer (MCA) used to acquire data was gradually set to 70 V and the angle between the top two detectors was $165 ^{\circ}$.

@@

The spectrum obtained for the triple source was the following:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/Calib.png}
    \captionof{figure}{Spectrum of the Calibration source}
\end{center}

>>>>

%\subsection{Procedure}
%    \label{sec:procedure}
%
%We started by displaying the samples in a vertical sample holder with the given order: in the lowest position the implanted sample, followed by lithium aluminate ($\ce{LiAlO2}$) and finally lithium fluoride ($\ce{LiF}$). 
%In order to do a calibration we added a triple $\alpha$ source on the holder above the lithium fluoride. 
%Using a pachymeter, we measured the distance between the samples so that afterwards we could control the height of the holder in the chamber and change the beam's target.
%We placed the sample holder on a support and inserted both of them inside the chamber. 
%A vacuum machine was connected to the accelerator to reduce the pressure inside both the chamber and the beam.
%Afterwards, we started the procedure to turn on the TANDEM accelerator, according to the provided instruction manual. 
%Firstly, we turned on the $\ce{H^+}$ duoplasmatron source of the accelerator as well as the magnets and lenses. 
%Then, we opened the valves to propagate the vacuum throughout the entirety of the tubes.
%In the control panel, we adjusted the angles of the lenses and the magnets current according to the manual, so that the beam would reach the samples. 
%Finally, we used a collimator with a 2mm radius to collimate the beam.
%In order to collect the data, we used a computer program to obtain the spectra of the different sources. 
%The multichannel analyzer (MCA) used to acquire data was gradually set to 70 V and the angle between the top two detectors was $165 ^{\circ}$.

@@

The spectrum obtained for the triple source was the following:
%Ea quis voluptate nisi culpa. Pariatur ad nostrud magna et. Occaecat tempor deserunt enim enim Lorem fugiat magna sint. Occaecat duis occaecat dolore cupidatat qui laboris reprehenderit. Dolor mollit sit tempor labore ad veniam adipisicing duis magna et duis.
%Sunt nostrud in dolor tempor minim velit incididunt Lorem adipisicing ullamco ad qui ad. Veniam magna anim Lorem in ad id qui Lorem ex cillum. Laboris cillum ad anim dolore non aute commodo. Nulla commodo reprehenderit mollit adipisicing do cupidatat proident. Adipisicing eu id incididunt tempor ad fugiat ullamco sit aliqua nulla ut duis labore nostrud. Nostrud deserunt excepteur ex et adipisicing nostrud sint dolor laboris nisi reprehenderit esse eu. Ex non fugiat mollit exercitation minim enim id ipsum velit reprehenderit ea proident nisi.
\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.3]{../../images/Calib.png}
    \vspace{-5mm}
    \captionof{figure}{Spectrum of the Calibration source}
\end{center}
